Geometric variational problems

### 2020-11-13 NSF2020/Description/background.tex
RJR

The equations~\eqref{HAP} and~\eqref{SL} possess a number of the mathematical properties
that mirror the phenomenological characteristics of hydrophobic attraction.
Specifically, solutions of~\eqref{SL} yield an attractive interaction between
hydrophobic bodies separated by water~\cite{Eriksson1989}.
Using boundary layer analysis, the HAP converges to a surface energy in the zero-decay length
limit~\cite{Lee2018, Lin2015, Shibata2004}.
Finally, we have demonstrated that the forces derived from HAP theory are non-additive~\cite{Meyer2006, Fu2018_SIAM}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

>>>>

The equations~\eqref{HAP} and~\eqref{SL} possess a number of the mathematical properties
that mirror the phenomenological characteristics of hydrophobic attraction.
Specifically, solutions of~\eqref{SL} yield an attractive force between
hydrophobic bodies separated by water, and this attraction 
decreases exponentially with the distance of separation~\cite{Eriksson1989}.
Using boundary layer analysis, the HAP converges to a surface energy in the zero-decay length
limit~\cite{Lee2018, Lin2015, Shibata2004}.
Finally, we have demonstrated that the forces derived from HAP theory are non-additive~\cite{Meyer2006, Fu2018_SIAM}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.
